\documentclass[12pt]{article} % Default font size
%!TEX program = xelatex
\input{structure.tex} % Include the file specifying document layout
\usepackage{comment}
\usepackage{xeCJK} %调用 xeCJK 宏包
\setCJKmainfont{SimSun} %设置 CJK 主字体为 SimSun （宋体）
\usepackage{etaremune}
\renewcommand{\labelenumi}{\theenumi)}
%-----------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

%\title{Lin Zhou (周琳)} % Print the main header
\title{Lin Zhou} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabular}{lp{13cm}}
%Website: &http://zl19920612.wixsite.com/linzhou\\
Website:&http://shi.buaa.edu.cn/zhoulin/en/index/162292/list/index.htm\\
Emails: & lzhou@buaa.edu.cn (Official)\\
&lzhou\_bhu@outlook.com (recommended)\\
&lzhou@u.nus.edu (lifelong) \\
Position: & Associate Professor, School of Cyber Science and Technology, Beihang University (BUAA)\\
Address: & Room 507, No. 37, Xueyuan Road, Haidian district, Beijing, China, 100037\\
\end{tabular}}

\section{Research Interests}
\begin{itemize}
\item Information theory and its applications
\item Space-air-ground integrated communications
\item Statistical signal processing
\item Physical layer security
\end{itemize}
% \begin{itemize}
% \item Refined asymptotics for network information theory
% \begin{itemize}
% \item Gray-Wyner problem
% \item Successive refinement problem
% \item Kaspi (with encoder side information) and Fu-Yeung problems
% \item ​Lossy multi-connectivity
% \end{itemize}
% \item Mismatched coding
% \begin{itemize}
% \item Rate-distortion saddle-point problem
% \item Robust and mismatched joint source-channel coding scheme
% \end{itemize}
% \item Streaming communication
% \begin{itemize}
% \item Streaming compression of correlated sources
% \end{itemize}
% \item Strong converse analyses
% \begin{itemize}
% \item Content identification with lossy recovery
% \item Hypothesis testing with communication constraints
% \item Successive refinement with causal decoder side information
% \end{itemize}
% \item Detection and inference
% \begin{itemize}
% \item Statistical classification
% \item Distributed detection with observed statistics
% \end{itemize}
% \end{itemize}


\section{Education}
\begin{tabular}{rp{11cm}}	
Aug. 2014 to Aug. 2018 & Ph.D., Department of Electrical and Computer Engineering (ECE) \\
 & \textbf{National University of Singapore (NUS)},~GPA: 4.92/5.0\\
 %& Thesis Title: On Multiterminal Source Coding: Refined Asymptotics, Mismatch and Streaming\\
 &Advisors: Prof. Vincent Y. F. Tan and Prof. Mehul Motani\\
 \\
Sept. 2010 to Jul. 2014 & Bachelor, Department of Information Engineering \\
& \textbf{Shanghai Jiao Tong University (SJTU)},~GPA: 3.63/4.0\\
%& Final Year Project Supervisor: Prof. Meixia Tao
\end{tabular}


\section{Research Experiences}
\begin{tabular}{rp{11cm}}
Aug. 2020 to present& ``Zhuobai'' project, Associate Professor, School of Cyber Science and Technology, Beihang University, Beijing, China\\	
\\
Jan. 2019 to Aug. 2020 & Research Fellow, Department of Electrical Engineering and Computer Science (EECS), University of Michigan, Ann Arbor, MI, USA\\
\vspace{.1in}
&Worked with Prof. Alfred Hero on fundamental limits and practical algorithms of machine learning problems.\\
Sept. 2018 to Dec. 2018 & Research Fellow, Department of ECE, NUS, Singapore\\
\vspace{.1in}
 & Worked with Prof. Vincent Y. F. Tan and Prof. Mehul Motani on fundamental limits of statistical inference and detection.\\
Mar. 2018 to Aug. 2018 & Research Engineer, Department of ECE, NUS, Singapore\\
\vspace{.1in}
 & Worked with Prof. Vincent Y. F. Tan and Prof. Mehul Motani on fundamental limits of statistical inference and detection.
\end{tabular}

\section{Preprints}
\begin{etaremune}
\item \textbf{Lin Zhou} and Alfred Hero, ``Resolution Limits of Non-Adaptive 20 Questions Search Strategies for a Moving Target'', To be submitted to IEEE Transactions on Information Theory.
\item \textbf{Lin Zhou} and Alfred Hero, ``Resolution Limits of Non-Adaptive 20 Questions Search for Multiple Targets'', Submitted to IEEE Transactions on Information Theory in Jan. 2021.
\item \textbf{Lin Zhou}, Yun Wei and Alfred Hero, ``Second-Order Asymptotically Optimal Universal Outlying Sequence Detection with Reject Option'', Submitted to IEEE Transactions on Information Theory in Sept. 2020.
\end{etaremune}

\section{Journal Papers}
%Total: 14
%TIT (CCF A, JCR Q2): 9, first: 8, second: 1
%Entropy (JCR Q3): 2, first: 1, corresponding: 1
%JSAC (JCR Q1, Top Journal): 1, first:1
%TIFS: 1, first: 1
%Information and Inference 1, first: 1
\begin{etaremune}
\item \textbf{Lin Zhou} and Daming Cao, ``Privacy-Utility Tradeoff for Hypothesis Testing  Over A Noisy Channel'', To appear in IEEE Transactions on Information Forensics and Security.
\item \textbf{Lin Zhou} and Alfred Hero, ``Resolution Limits of Non-Adaptive Noisy 20 Questions Problem'', IEEE Transactions on Information Theory, Vol: 67, No: 4, Pages: 2055-2073, 2021.
\item Haiyun He, \textbf{Lin Zhou} and Vincent Y. F. Tan, ``Distributed Detection with Empirically Observed Statistics'', IEEE Transactions on Information Theory, Vol: 66, No: 7, Pages 4349--4367, 2020.
\item \textbf{Lin Zhou}, Vincent Y.\ F.\ Tan and Mehul Motani,  ``Second-Order Asymptotically Optimal Statistical Classification'', Information and Inference: A Journal of IMA, Volume: 9, Issue: 1, Pages: 81--111, 2020.
\item \textbf{Lin Zhou}, ``Multiple Private Key Generation for Continuous Memoryless Sources with A Helper'', Volume: 15, Pages: 2629--2640, IEEE Transactions on Information Forensics and Security, 2020.
\item Daming Cao, \textbf{Lin Zhou} and Vincent Y. F. Tan, ``A Strong Converse Theorem for Hypothesis Testing Against Independence over a Two-Hop Network'', Entropy 2019, Volume: 21, Issue: 12, Article 1171, special issue on multiuser Information Theory II.
\item \textbf{Lin Zhou} and Mehul Motani,  ``Non-Asymptotic Converse Bounds and Refined Asymptotics for Two Lossy Source Coding Problems'', IEEE Transactions on Information Theory, Volume: 65, Issue: 10, Pages: 6414-6440, 2019.
\item \textbf{Lin Zhou}, Vincent Y.\ F.\ Tan and Mehul Motani,  ``Refined Asymptotics for Rate-Distortion using Gaussian Codebooks for Arbitrary Sources'', IEEE Transactions on Information Theory, Volume: 65, Issue: 5, Pages: 3145--3159, 2019.
\item \textbf{Lin Zhou}, Vincent Y.\ F.\ Tan and Mehul Motani,  ``The Dispersion of Mismatched Joint Source-Channel Coding for Arbitrary Sources and Additive Channels'', IEEE Transactions on Information Theory, Volume: 65, Issue: 4, Pages: 2234--2251, 2019.
\item \textbf{Lin Zhou}, Albrecht Wolf and Mehul Motani,  ``On Lossy Multi-Connectivity: Finite Blocklength Performance and Second-Order Asymptotics'', IEEE Journal on Selected Areas in Communication (JSAC), Volume: 37, Issue: 4, Pages: 735--748, 2019, special issue on ultra-reliable and low-latency communication (URLLC).
\item \textbf{Lin Zhou} and Alfred Hero, ``Exponential Strong Converse for Successive Refinement with Causal Decoder Side Information'', Entropy 2019, Volume: 21, Issue: 4, Article 410, special issue on multiuser Information Theory II.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan, Lei Yu and Mehul Motani,  ``Exponential Strong Converse for Content Identification with Lossy Recovery'', IEEE Transactions on Information Theory, Volume: 64, Issue: 8, Pages: 5879--5897, 2018.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani,  ``Achievable Moderate Deviations Asymptotics for Streaming Compression of Correlated Sources'', IEEE Transactions on Information Theory, Volume: 64, Issue: 5, Pages: 3756--3780, 2018.
\item \textbf{Lin Zhou}, Vincent Y.\ F.\ Tan and Mehul Motani,  ``Second-Order and Moderate Deviation Asymptotics for Successive Refinement'', IEEE Transactions on Information Theory, Volume: 63, Issue: 5, Pages: 2896--2921, 2017.
\item \textbf{Lin Zhou}, Vincent Y.\ F.\ Tan and Mehul Motani,  ``Discrete Lossy Gray-Wyner Revisited: Second-order Asymptotics, Large and Moderate Deviations'', IEEE Transactions on Information Theory, Volume: 63, Issue: 3, Pages: 1766--1791, 2017.
\end{etaremune}


\section{Conference Papers}
\begin{etaremune}
\item Lin Bai, Zhuangfei Wu and \textbf{Lin Zhou}, ``Achievable Second-Order Asymptotics for Successive Refinement Using Gaussian Codebooks'', ISIT 2021, LA, USA (Virtual).
\item \textbf{Lin Zhou} and Alfred Hero, ``Achievable Resolution Limits for the Noisy Adaptive 20 Questions Problem'', ISIT 2021, LA, USA (Virtual).
\item \textbf{Lin Zhou} and Alfred Hero, ``Resolution Limits of Non-Adaptive 20 Questions Search for Multiple Targets'',  ISIT 2021, LA, USA (Virtual).
\item \textbf{Lin Zhou} and Alfred Hero, ``Resolution Limits of 20 Questions Search Strategies for Moving Targets'', IEEE ICASSP, Toronto, Canada, 2021 (virtual).
\item \textbf{Lin Zhou} and Alfred Hero, ``Resolution Limits of Non-Adaptive Querying for Noisy 20 Questions Estimation'', IEEE ISIT, Los Angeles, USA, 2020 (virtual).
\item Haiyun He, \textbf{Lin Zhou} and Vincent Y. F. Tan, ``Distributed Detection with Empirically Observed Statistics'', IEEE ITW, Visby, Gotland, Sweden, 2019.
\item \textbf{Lin Zhou} and Alfred Hero, ``Exponential Strong Converse for Successive Refinement with Causal Decoder Side Information'', IEEE ISIT, Paris, France, 2019.
\item Daming Cao, \textbf{Lin Zhou} and Vincent Y. F. Tan, ``Strong Converse for Hypothesis Testing Against Independence over a Two-Hop Network'', IEEE ISIT, Paris, France, 2019.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani, ``Second-Order Asymptotically Optimal Statistical Classification'', IEEE ISIT, Paris, France, 2019.
\item \textbf{Lin Zhou}, Albrecht Wolf and Mehul Motani, ``On the Finite Blocklength Performance of Lossy Multi-Connectivity'', IEEE Globecom, Abu Dhabi, UAE, 2018.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani,  ``Second-Order Asymptotics of Universal JSCC for Arbitrary Sources and Additive Channels'', IEEE ISIT, Colorado, USA, 2018.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani, ``Second-Order Asymptotics of Rate-Distortion using Gaussian Codebooks for Arbitrary Sources'', IEEE ISIT, Colorado, USA, 2018.
\item \textbf{Lin Zhou} and Mehul Motani, ``On the Multiple Description Coding with One Semi-deterministic Distortion Measure'', IEEE Globecom, Singapore, 2017.
\item \textbf{Lin Zhou} and Mehul Motani,  ``Kaspi Problem Revisited: Non-Asymptotic Converse Bound and Second-Order Asymptotics'', IEEE Globecom, Singapore, 2017.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani,  ``Strong Converse for Content Identification with Lossy Recovery'', IEEE ISIT, Aachen, Germany, 2017.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani, ``Achievable Moderate Deviations Asymptotics for Streaming Compression of Correlated Sources'', IEEE ISIT, Aachen, Germany, 2017.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani,  ``Second-Order Coding Region for the Discrete Successive Refinement Source Coding Problem'', IEEE ISIT, Barcelona, Spain, 2016.
\item \textbf{Lin Zhou}, Vincent Y. F. Tan and Mehul Motani, ``Second-Order Coding Region for the Discrete Lossy Gray-Wyner Source Coding Problem'', IEEE ISIT, Barcelona, Spain, 2016.
\end{etaremune}



\section{Honors \& Awards}
\begin{tabular}{rp{10cm}}
Aug. 2014 to Mar. 2018 & NUS Research Scholarship\\
2016--2018 &ISIT Student Travel Award\\
2013 &Second Prize for Undergraduate Mathematical Contest in Modeling, Shanghai Branch Zone of China \\
%May 2013 & Second Prize in College Student Innovation Competition on Circuit and System Application of Texas Instrument China \\
2011, 2012, 2013 & Academic Excellence Scholarship in SJTU
\end{tabular}

\section{Invited Talks}
\begin{itemize}
\item Information theory, inference and learning with low-latency and high reliability
\begin{itemize}
\item Mar. 2020, Department of Engineering, \textbf{University of Cambridge}
\end{itemize}

\item Information theory and its applications in statistical inference
\begin{itemize}
\item Apr. 2019, School of Statistics and Data Science, \textbf{Nankai University}
\item Jan. 2020, Department of Computer Science, \textbf{Southern University of Science and Technology}
\end{itemize}
\item Lossy source coding using Gaussian codebooks
\begin{itemize}
\item Dec. 2019, School of Cyber Science and Technology, \textbf{Beihang University}
\item Dec. 2019, Department of Communication Science and Engineering, \textbf{Fudan University}
\end{itemize}

\end{itemize}

\section{Professional Services}
\begin{itemize}
\item Session chair for
\begin{itemize}
\item Source coding session, ITW 2018, Guangzhou, China
\end{itemize}
\item Reviewer for
% \begin{itemize}
% \item Journals: IEEE Transactions on Information Theory (TIT), IEEE Journal on Selected Areas in Communications (JSAC), IEEE Journal of Selected Topics in Signal Processing (JSTSP), IEEE Transactions on Communications (TCOM), IEEE Transactions on Signal Processing (TSP), MDPI Entropy, MDPI Algorithms, IEEE Communications Letter, IEEE Access, IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, Physical Communication
% \item Conferences: ISIT 2016-2020, ITW 2017-2019, EUSIPCO 2019-2020, IZS 2018, ISITA 2018, ICITS 2017, ICC 2015
% \end{itemize}
%13 journals and 7 conferences
\begin{itemize}
\item Journals
\begin{enumerate}
\item IEEE Transactions on Information Theory (TIT)
\item IEEE Journal on Selected Areas in Information Theory (JSAIT)
\item IEEE Journal on Selected Areas in Communications (JSAC)
\item IEEE Journal of Selected Topics in Signal Processing (JSTSP)
\item IEEE Transactions on Wireless Communications (TWC)
\item IEEE Transactions on Communications (TCOM)
\item IEEE Transactions on Signal Processing (TSP)
\item IEEE Transactions on Cognitive Communications and Networking (TCCN)
\item Journal of Communications and Information Networks (JCIN)
\item IEEE Wireless Communications Magazine (WCM)
\item IEEE Communications Letter (CL)
\item IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences
%\item IEEE Access
\item MDPI Entropy
\item MDPI Algorithms
\item MDPI Applied Sciences
\item MDPI Electronics
\item Elesvier Physical Communication
\end{enumerate}
\item Conferences:
\begin{enumerate}
\item International Symposium on Information Theory (ISIT) 2016-2021
\item Information Theory Workshop (ITW) 2017-2021
\item European Signal Processing Conference (EUSIPCO) 2019-2021
\item Iran Workshop on Communications and Information Theory (IWCIT) 2021
\item International Zurich Seminar (IZS) 2018
\item International Symposium on Information Theory and its Applications (ISITA) 2018
\item International Conference on Information Theoretic Security (ICITS) 2017
\item International Conference on Communications (ICC) 2015
\end{enumerate}
\end{itemize}
\item Volunteer for 
\begin{itemize}
\item ISITA 2018, Singapore
\end{itemize}
\end{itemize}

\section{Teaching Experience}

\begin{tabular}{lr}
Lecturer&Spring 2021\\
B3I393160 Principles of Communications&BUAA\\
Lecturer&Spring 2021\\
Introduction of Wireless Communications&BUAA\\
Lecturer&Winter 2020\\
B3J394210 Technical English&BUAA\\
Graduate Teaching Assistant&Winter 2015, 2016\\
EE2032: Signals and Communications Design Lab& NUS\\
Graduate Teaching Assistant&Summer 2015, 2016\\
EE3204: Computer and Communications Network Lab& NUS\\
Graduate Teaching Assistant&Winter 2016\\
EE3131C: Communications Systems& NUS\\
\end{tabular}


% \section{Student Supervision}
% \begin{itemize}
% \item Daming Cao, vising Ph.D. student at NUS
% \begin{itemize}
% \item Project: Strong converse for hypothesis testing with communication constraints
% \item Publications: Preprint [2]
% \end{itemize}
% \item Haiyun He, Ph.D. student at NUS
% \begin{itemize}
% \item Project: Distributed detection with empirically observed statistics
% \item Publications: Preprint [4]
% \end{itemize}
% \end{itemize}


% \section{Referees}
% \begin{itemize}
% \item Prof. Alfred Hero, University of Michigan, hero@eecs.umich.edu
% \item Prof. Vincent Y. F. Tan, National University of Singapore, vtan@nus.edu.sg
% \item Prof. Mehul Motani, National University of Singapore, motani@nus.edu.sg
% \item Prof. Jun Chen, McMaster University, junchen@ece.mcmaster.ca 
% \item Prof. Shun Watanabe, Tokyo University of Agriculture and Technology, shunwata@cc.tuat.ac.jp
% \item Prof. Meixia Tao, Shanghai Jiao Tong University, mxtao@sjtu.edu.cn
% \end{itemize}
%----------------------------------------------------------------------------------------
\end{document}